Introduction to linear regression

### 2018-11-15 DATA606/Lab7/michael-simple_regression.Rmd
Work on Lab 7
More work on lab 7

1.  What type of plot would you use to display the relationship between `runs` 
    and one of the other numerical variables? **A scatter plot.** Plot this 
    relationship using the variable `at_bats` as the predictor. 
    ```{r}
    plot(mlb11$at_bats, mlb11$runs)
    ```
    Doe the relationship look linear? **Yes it looks somewhat linear.** If you knew a
    team's `at_bats`, would you be comfortable using a linear model to predict the 
    number of runs? **I don't know if I would.**

@@

5.  If a team manager saw the least squares regression line and not the actual 
    data, how many runs would he or she predict for a team with 5,578 at-bats?
    $\hat{y} = -2789.2429 + 0.6305 * atbats = -2789.2429 + 0.6305 * 5578 = -2789.2429 + 3516.929 = 727.6861$
    Is this an overestimate or an underestimate, and by how much? In other 
    words, what is the residual for this prediction?

>>>>

1.  What type of plot would you use to display the relationship between `runs` 
    and one of the other numerical variables? **A scatter plot.** Plot this 
    relationship using the variable `at_bats` as the predictor. 
    ```{r}
    plot(mlb11$at_bats, mlb11$runs)
    ```

    Does the relationship look linear? **Yes it looks somewhat linear.** If you knew
    a team's `at_bats`, would you be comfortable using a linear model to predict the 
    number of runs? **I don't know if I would.**

@@

5.  If a team manager saw the least squares regression line and not the actual 
    data, how many runs would he or she predict for a team with 5,578 at-bats?
    $\hat{y} = -2789.2429 + 0.6305 * atbats = -2789.2429 + 0.6305 * 5578 = -2789.2429 + 3516.929 = 727.6861$
    Is this an overestimate or an underestimate, and by how much? In other words, 
    what is the residual for this prediction? 
    ```{r message=FALSE, echo=FALSE}
    library(dplyr)
    test <- mlb11 %>%
      mutate(diff = abs(at_bats - 5578)) %>%
      mutate(closest = min(diff)) %>%
      filter(closest == diff) %>%
      select(at_bats, runs) 
    ```
    **The closest data we have is `r test$at_bats`.   For this case the model predicts `r round(predict(m1, test), 0)` runs and the actual was `r test$runs`.  The residual is `r round(test$runs - predict(m1, test), 0)` runs which indicates the model was an overestimate.  It would be similar to 5,578 at bats.**
